Global Value Chain Analysis of LMICs

### 2015-04-22 OECD-TiVa-LMIC-GVCs.Rmd
reorder slides

---
title: "Global Value Chain Analysis of LMICs"
author: "Victor Kummritz and Bastiaan Quast"
date: "April 22, 2015"
output: ioslides_presentation
---

@@

## New Toolbox and Indicators: decompr and gvc
Exemplary indicators:

- I2E (importing-to-export, based on Hummels et al. 1998): The foreign value added content of domestic exports.
    - I2E_LMIC: The foreign value added content sourced in low- and middle income   countries
    - etc.
- E2R (exporting-to-reexport, based on Hummels et al. 1998): The domestic value added content of foreign exports.
- NRCA (New revealed comparative advantage, based on Wang, Wei, and Zhu 2014): Revealed comparative advantage measure based on value added data.

## An application to new data: ICIOS covering LMICs

@@

- LMICs

@@

@@

## An application to new data: Confirming stylized facts
The growth of GVC participation.
```{r, echo=FALSE}
gvc_indicators %>%
  group_by(year) %>%
  summarise(e2r = sum(dvar_ik) / sum(exports_ik),
            i2e = sum(fvax_ams_ik) / sum(exports_ik) ) %>%
  ggvis(~year, ~e2r ) %>%
  layer_lines(stroke="e2r") %>%
  layer_lines(~year, ~i2e, stroke="i2e")
```

## An application to new data: Confirming stylized facts
The expansion of GVCs.
```{r, echo=FALSE}
w1995_2008 %>%
  group_by(year) %>%
  summarise( RDV = sum(RDV_INT) + sum(RDV_FIN) + sum(RDV_FIN2),
             PDC = sum(DDC_FIN) + sum(DDC_INT) + sum(ODC) + sum(MDC) ) %>%
  ggvis(~year, ~RDV, stroke="RDV") %>%
  layer_lines() %>%
  layer_lines(~year, ~PDC, stroke="PDC")
```

@@

```{r, echo=FALSE}
gvc_indicators %>%
  group_by(ind_name) %>%
  summarise(i2e = sum(fvax_ams_ik) * 100 / sum(exports_ik) ) %>%
  top_n(10) %>%
  ggvis(~factor(ind_name), ~i2e) %>%
  layer_bars() %>%
  add_axis("x", title = "industry name")
```

```{r, echo=FALSE}
gvc_indicators %>%
  group_by(ind_name) %>%
  summarise(e2r = sum(dvar_ik) * 100 / sum(exports_ik) ) %>%
  top_n(10, e2r) %>%
  ggvis(~factor(ind_name), ~e2r) %>%
  layer_bars() %>%
  add_axis("x", title = "industry name")
```

```{r, echo=FALSE}
gvc_indicators %>%
  group_by(ctry) %>%
  summarise(i2e = sum(fvax_ams_ik) / sum(exports_ik) ) %>%
  top_n(10, i2e) %>%
  ggvis(~factor(ctry), ~i2e ) %>%
  layer_bars()
```

@@

## General Stylised Facts

 - section 3.1 of wwz
 - growth of GVC trade
 - length of GVC
 - determinants of an industry's participation
 - determinants of a country's participation
 - trade balanses in VA terms differ substantially from those in gross terms

## I2E

  ```{r, echo=FALSE}
 gvc_indicators %>%
  group_by(year, ic) %>%
  summarise(i2e = sum(fvax_ams_ik) / sum(exports_ik) ) %>%
  ggvis(~year, ~i2e, stroke = ~ic ) %>%
  layer_lines()
 ```

## GVCs of LMICs

 - stylised facts for LMICs
 - source / using countries specific indicators for LMICs
 - nrca and trca of LMIC
 - fvafin vs. fvaint for LMICs (WWZ 3.3)
 - dvix decomposition (WWZ 3.4)

@@

```{r, echo=FALSE} 
# TRCA vs NRCA for China, ELQ
gvc_indicators %>%
  filter(ctry == "chn") %>%
  filter(ind_name == "elq") %>%
  group_by(year) %>%
  summarise( trca = sum(rca), nrca = sum(nrca) ) %>%
  ggvis(~year, ~trca, stroke = "trca") %>%
  layer_lines() %>%
  layer_lines(~year, ~nrca, stroke="nrca")
```

>>>>

---
title: "Global Value Chain Analysis of LMICs"
author: "Victor Kummritz and Bastiaan Quast"
date: "April 22, 2015"
output:
  ioslides_presentation:
    fig_height: 3
    fig_retina: null
    fig_width: 5
---

@@

## New Toolbox and Indicators: decompr and gvc

Indicators:

- I2E (importing-to-export, based on Hummels et al. 1998): The foreign value added content of domestic exports.
- E2R (exporting-to-reexport, based on Hummels et al. 1998): The domestic value added content of foreign exports.
- NRCA (New revealed comparative advantage, based on Wang, Wei, and Zhu 2014): Revealed comparative advantage measure based on value added data.

## An application to new data: ICIOs covering LMICs

@@

- Low- and Middle-Income Countries (LMICs)

## package: decompr

@@

## package: gvc

@@

## The expansion of GVCs

```{r, echo=FALSE}
w1995_2008 %>%
  group_by(year) %>%
  summarise( RDV = sum(RDV_INT) + sum(RDV_FIN) + sum(RDV_FIN2),
             PDC = sum(DDC_FIN) + sum(DDC_INT) + sum(ODC) + sum(MDC) ) %>%
  ggvis(~year, ~RDV, stroke="RDV") %>%
  layer_lines() %>%
  layer_lines(~year, ~PDC, stroke="PDC")
```

## The growth of GVC participation.

```{r, echo=FALSE}
gvc_indicators %>%
  group_by(year) %>%
  summarise(e2r = sum(dvar_ik) / sum(exports_ik),
            i2e = sum(fvax_ams_ik) / sum(exports_ik) ) %>%
  ggvis(~year, ~e2r ) %>%
  layer_lines(stroke="e2r") %>%
  layer_lines(~year, ~i2e, stroke="i2e")
```

## GVC participation by *IC: I2E
Importing to Export (I2E)

```{r, echo=FALSE}
# i2e by year, ic
gvc_indicators %>%
  group_by(year, ic) %>%
  summarise(i2e = sum(fvax_ams_ik) / sum(exports_ik) ) %>%
  ggvis(~year, ~i2e, stroke = ~ic ) %>%
  layer_lines()
```

## GVC participation by *IC: E2R
Exporting to Re-export (E2R)

```{r, echo=FALSE}
# e2r by year, ic
gvc_indicators %>%
  group_by(year, ic) %>%
  summarise(e2r = sum(dvar_ik) / sum(exports_ik) ) %>%
  ggvis(~year, ~e2r, stroke = ~ic ) %>%
  layer_lines()
```

@@

```{r, echo=FALSE, }
gvc_indicators %>%
  group_by(ctry) %>%
  summarise(i2e = sum(fvax_ams_ik) / sum(exports_ik) ) %>%
  top_n(10, i2e) %>%
  ggvis(~factor(ctry), ~i2e ) %>%
  layer_bars()
```

@@

@@

```{r, echo=FALSE, } 
# TRCA vs NRCA for China, ELQ
gvc_indicators %>%
  filter(ctry == "chn") %>%
  filter(ind_name == "ceq") %>%
  group_by(year) %>%
  summarise( trca = sum(rca), nrca = sum(nrca) ) %>%
  ggvis(~year, ~trca, stroke = "trca") %>%
  layer_lines() %>%
  layer_lines(~year, ~nrca, stroke="nrca")
```
